### 2014-10-21 PrivacyProtection-2014-09-09.tex
added figure for implicit sensor privacy matrix, fixed some errors

Although we use Fried's definition of privacy as one's control over information about oneself, we do not feel safe relying only on that to conduct a privacy protection analysis.
We need additional means to analyze in more detail which aspects of our lives need protection.
Friedewald, Finn and Wright \cite{7ToP} introduced a privacy taxonomy called \textit{Seven Types of Privacy} that can be of help.
The seven types of privacy are an extension to the four types of privacy by Roger Clarke \cite{RClarke:4ToP}:
\begin{itemize}
\item Privacy of the Person
\item Privacy of Personal Behaviour
\item Privacy of Personal Communication
\item Privacy of Personal Data
\end{itemize}
However, Friedewald et al. felt that Clarke's taxonomy are technologically outdated and no longer adequate.
In order to fix this they extend the former four to the now introduced seven types privacy as follows:

@@

%\includegraphics{../diagrams/png/sensor-privacy-matrix.png}
\input{./figures/LG-Sensor-Privacy-Matrix}

>>>>

Although we use Fried's definition of privacy as one's control over information about oneself, we do not feel safe conducting a privacy protection analysis relying only him.
We need additional means to analyze in more detail which aspects of our lives need protection.
Friedewald, Finn and Wright \cite{7ToP} introduced a privacy taxonomy called \textit{Seven Types of Privacy} that can be of help.
The seven types of privacy are an extension to the four types of privacy by Roger Clarke \cite{RClarke:4ToP}:
\begin{itemize}
\item Privacy of the Person
\item Privacy of Personal Behaviour
\item Privacy of Personal Communication
\item Privacy of Personal Data
\end{itemize}
However, Friedewald et al. felt that Clarke's taxonomy is technologically outdated and no longer adequate.
In order to fix this they extend the former four to the now introduced seven types privacy as follows:

@@

%\includegraphics{../diagrams/png/sensor-privacy-matrix.png}
\input{./figures/LG-Sensor-Privacy-Matrix}
\input{./figures/LG-Implicit-Sensor-Privacy-Matrix}
